First Order Alternation

### 2018-11-07 quantifiers/body.tex
ok

As applications of first order alternating automata, we identified
several undecidable but recursively enumerable problems, for which no
effective methods exist, to date: inclusion between recognizable timed
languages \cite{AlurDill94} and between languages recognized by
finite-memory automata \cite{KaminskiFrancez94}, as well as emptiness
of predicate automata, a model of first-order alternating automata
used to check safety and liveness properties of parameterized
concurrent programs \cite{Farzan15,Farzan16}.

>>>>

As applications of first order alternating automata, we identified
several undecidable, for which no semi-algorithmic methods exist:
inclusion between recognizable timed languages \cite{AlurDill94}, 
between languages recognized by finite-memory automata
\cite{KaminskiFrancez94} and emptiness of predicate automata,
a model of first-order alternating automata used to check safety and
liveness properties of parameterized concurrent programs
\cite{Farzan15,Farzan16}.

For reasons of space, all proofs of technical results in this paper
are given in \cite{IosifXu18ArXiv}.
